Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
finished design section

\noindent {\bfseries Overview}
{\color {red}
%improve what is below:
For users to circumvent censorship in their resident countries, they will need
to configure Tor to set up a proxy, bridge, or both. There is a configuration
wizard to help guide users through setting up their connection, but

Our hypothesis is that the average user does not have knowledge
knowledge on how certain pluggable transports work, or to provide non-publicly listed IP
addresses bridges. Certain real-world censorship settings require the user to provide this
information during configuration, which will affect how successful users are at 
circumventing censorship using Tor. There are blogs in countries which have extensive
censorship on how to configure Tor correctly {\color {red} cite something}, and participants may 
receive additional informatio through word of mouth. Our study will measure if the configuration
interface successfully guides users to correctly configuring their browser, not accounting 
for any additional  information that a real user may have.}\\

>>>>

\noindent {\bfseries Overview}
There is a configuration interface (Figure ~\ref{fig:interface}) to help guide users through 
setting up their connection to the Tor network. Through this, users can configure Tor to set up a bridge,
proxy, or both. Since proxies are not a Tor-specific notion nor explicitly required to circumvent censorship, 
we will focus our study on bridge configuration. We accomplish this by placing users in crafted simulated 
censorship environments which require particular bridge configurations to circumvent censorship.

Our hypothesis is that the average user does not have knowledge
knowledge on how certain pluggable transports work, or to provide non-publicly listed IP
addresses bridges. Certain real-world censorship settings require the user to provide this
information during configuration, which will affect how successful users are at 
circumventing censorship using Tor. There are blogs in countries which have extensive
censorship on how to configure Tor correctly {\color {red} cite something}, and participants may 
receive additional informatio through word of mouth. Our study will measure if the configuration
interface successfully guides users to correctly configuring their browser, not accounting 
for any additional  information that a real user may have.\\
